\section{Introduction To Project} 
Retinal fundus images provide rich information of pathological changes which may indicate
diseases such as arteriosclerosis, diabetes, hypertension, stroke, and cardiovascular disease.
the project will help doctors and medical technicians to get better assessment of the image
and so that they can help the patient with their diagnosis. We used DRIVE database for the
sample retinal imagesand we will apply various enhancement techniques and provide qualitative
analysis of given images.

\section{Project Category(Internet based, Application or System Development)}
This application is research based application .

\section{Objectives}

\begin{itemize}
	\item  To study the enhancement of retinal image.

	\item To process an retinal image so that the output image is more enhanced than the original image..
	
	\item To perform the objective evaluation of the result and tell about the best image.


\end{itemize}

\section{Problem Formulation}
Through our project, medical team or doctors will be able to give a better assessment of the images for the proper treatment of the various eye related problems and can help in find out about various eye realted diseases  .   

\section{Proposed System Modules}

\begin{itemize}
	\item User will be able to select retinal image for various image operations.

	\item Time will be saved as doctors will find the disease much faster through the image  .
	
	\item Medical team will give assesment about the best possible image.   
	
	
	


\end{itemize}

 
\section{Unique Features of the System}
\begin{itemize}

\item Time will be saved as doctors will find the disease much faster through the image  .
\item To process an retinal image so that the output image is more enhanced than the original image.

\item User will be able to select retinal image for various image operations..

\item Medical team will give assesment about the best possible image.

\end{itemize}


